---
title: "linear model from Web"
author: "Jessica Villa"
date: "Summer 2022."
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
lmr = lm(SIMS~ARM,data=data)
abline
```

The scatter plot is for model1 SIMS~ARMS. ARM is the X-Axis, and SIMS is the Y-Axis. The plot shows a
positive linear correlation.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation is 0.6860 the line is positive.


### Inferential  (Build model.1)

```{r}
summary(lmr)
newdata=c(GRIP=94, ARM=88)
```
Residuals show 1.226 on 145 degrees of freedom.
P-value 0.00000000000000022 Adjusted R-Squared is 0.467

#### Predict at target point

```{r}
predictSIM = predict.lm(lmr, newdata=data.frame(GRIP = 94, ARM = 88))
print(predictSIM)
```

Predicted target point is positive 0.71.

#### scatterplot with model fit
  
```{r}
plot(lmr)
```

The standardized residuals Normal Q-Q graph shows a positive correlation. The remaining plot graphs run
almost horizontal, or at zero slope.  

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
grip =lm(SIMS~GRIP,data=data)
abline (grip)
```

The scatter plot shows GRIP on the X-axis and SIMS on the Y-Axis. for SIM~GRIP shows a positive linear
correlation.


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation for SIMS~GRIP is 0.6398458 slightly smaller than the correlation between SIMS~ARM which
is 0.686073. Model1 is a better model

### Inferential  (Build model.2)
  
```{r}
summary(grip)
newdata=c(GRIP=94, ARM=88)
```

Residuals show 1.295 slightly higher than GRIP~ARM.
P-value 0.00000000000000022 and adjusted R-Sqaured is 0.4053.

#### predict model.2 at target point

```{r}
predictSIM = predict.lm(grip, newdata=data.frame(GRIP = 94, ARM = 88))
print(predictSIM)
```

The target point is -0.5361

#### now add the model fit to our plot for model.2
  
```{r}
plot(grip)
```

The standardized residuals Normal Q-Q graph shows a positive correlation. The remaining plot graphs show
a negative slope.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
data2=lm(SIMS~ARM+GRIP, data+data)
summary(data2)
```

The residual is 2.288 a number significantly higher than SIM~ARM and SIM~GRIP; however the Adjusted RSquared is the lowest when compared to Model1 and Model2.
P-value 0.0000000000000002 and adjusted R-Sqaured is 0.535
  
### Inferential  (Build 2-dimentional model.3)

Both ARM at 0.6860073 and GRIP at 0.6398458 show a positive correlation and close in value.

#### predict model.3 at target point
  
```{r}
predict.lm(data2, newdata =data.frame(GRIP =94, ARM = 88))
```

The target point is -5.2842

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(lmr,data2)
```
The Residual Degrees of Freedom (Res. Df) are 145. The Residual Sum of Squares (RSS) add up to 217 errors
were reduced by 29.45 there are less errors in model2. Therefore model 2 is the best m

### Model.2 vs Model.3

```{r}
anova(grip,data2)
```
The Residual Degree of Freedom (Res.Df) is 145. The Residual Sum of Squares (RSS) add up to All the
errors together add up to 243.07. The errors were reduced by 54.639. Model2 is a better model than model1
because more errors were corrected.

## Informally compare Model.1 with model.2
Model1 and model2 appear similar in that they are positive slope direction for the Standardized Residual
Normal Q-Q plot. The remaining plots appear to be closer to a zero slope.
The SIMS~GRIP correlation is 0.6398458 which is smaller than the SIMS~ARM correlation of 0.6860073 a
difference of 0.0461615. Both model1 and model2 have residuals degree of freedom of 145. Model1 has a
residual sum of squares of 217.88. Model2 has a residual sum of squares 243.07. The difference is
25.19.
