---
title: "linear model from Web"
author: "Jessica Villa"
date: "Summer 2022."
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
lmr = lm(SIMS~ARM,data=data)
abline
```

The scatter plot is for model1 SIMS~ARMS. ARM is the X-Axis, and SIMS is the Y-Axis. The plot shows a
positive linear correlation.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation is 0.6860 the line is positive.


### Inferential  (Build model.1)

```{r}
summary(lmr)
newdata=c(GRIP=94, ARM=88)
```
Residuals show 1.226 on 145 degrees of freedom.
P-value 0.00000000000000022 Adjusted R-Squared is 0.467

#### Predict at target point

```{r}
predictSIM = predict.lm(lmr, newdata=data.frame(GRIP = 94, ARM = 88))
print(predictSIM)
```

Predicted target point is positive 0.71.

#### scatterplot with model fit
  
```{r}
plot(lmr)
```

The standardized residuals Normal Q-Q graph shows a positive correlation. The remaining plot graphs run
almost horizontal, or at zero slope.  

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
grip =lm(SIMS~GRIP,data=data)
abline (grip)
```

The scatter plot shows GRIP on the X-axis and SIMS on the Y-Axis. for SIM~GRIP shows a positive linear
correlation.


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation for SIMS~GRIP is 0.6398458 slightly smaller than the correlation between SIMS~ARM which
is 0.686073. Model1 is a better model

### Inferential  (Build model.2)
  
```{r}
summary(grip)
newdata=c(GRIP=94, ARM=88)
```

Residuals show 1.295 slightly higher than GRIP~ARM.
P-value 0.00000000000000022 and adjusted R-Sqaured is 0.4053.

#### predict model.2 at target point

```{r}
predictSIM = predict.lm(grip, newdata=data.frame(GRIP = 94, ARM = 88))
print(predictSIM)
```

The target point is -0.5361

#### now add the model fit to our plot for model.2
  
```{r}
plot(grip)
```

The standardized residuals Normal Q-Q graph shows a positive correlation. The remaining plot graphs show
a negative slope.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

